Automatic word stress annotation of Russian running text (max 8 pages)

### 2015-01-19 rusaccent-nodalida-2015/rusaccent.tex
typos
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@58462 72bbbca6-d526-0410-a7d9-f06f51895060

For our baseline, we take the output of our morphological analyzer (without the 
Constraint Grammar) in combination with the {\small {\tt bare}}, 
{\small {\tt safe}}, {\small {\tt guess}} and {\small {\tt guessFreq}} 
approaches. We also compare our outcomes with the 
RussianGram\footnote{http://russiangram.com/} plugin 
for the Google Chrome web browser. RussianGram is not open-source, so we
can only guess what technologies support the service. In any case, it provides a
meaningful reference point for the success of each of the methods described 
above.

@@

Other studies have applied machine-learning to guessing stress of unknown words
\cite{Pearson.ea-00,Webster-04,Dou.ea-09,hall_sproat_russian_2013}. For example,
for unknown words, \newcite{hall_sproat_russian_2013} achieve an accuracy of 
83.9\%. Implementing a similar model in a rule-based system like ours would allow 
for some improvements to this result. Their model was trained on a full list of 
Russian words, which is not representative of the words that would be unknown to 
a system like ours. Most of the complicated wordstress patterns are a closed 
class\footnote{The growing number of masculine nouns with shifting stress 
(\emph{d\'{o}ktor$\sim$doktor\'{a}}) are an exception to this generalization.},
so we could exclude closed classes of words from the training data, leaving only
word classes that are likely to be similar to unknown tokens, such as those with 
productive derivational affixes.

Future work/potential applications:
Two sections: known words and unknown words
\begin{itemize}
\item As with any lexicon- and rule-based system, those components can be expanded and improved, especially considering the short span over which they were developed.
\item Another relevant issue is whether the ambiguity can be resolved at all. For example, when is stress marked in authentic by-native-for-native texts? A computer should not be expected to predict the stress on such words (although a computer could possibly identify words that should be marked for 
natives.)

\end{itemize}
%\section*{Acknowledgments}
%
%Do not number the acknowledgment section. Do not include this section
%when submitting your paper for review.

>>>>

For our baseline, we take the output of our morphological analyzer (without the 
Constraint Grammar) in combination with the {\small {\tt bare}}, 
{\small {\tt safe}}, {\small {\tt guess}}, {\small {\tt guessFreq}}, 
{\small {\tt guessSyll}}, and {\small {\tt guessFreqSyll}} approaches. We also 
compare our outcomes with the RussianGram\footnote{http://russiangram.com/} 
plugin for the Google Chrome web browser. RussianGram is not open-source, so we
can only guess what technologies support the service. In any case, it provides a
meaningful reference point for the success of each of the methods described 
above.

@@

Other studies have applied machine-learning to guessing stress of unknown words
\cite{Pearson.ea-00,Webster-04,Dou.ea-09,hall_sproat_russian_2013}. For example,
for unknown words, \newcite{hall_sproat_russian_2013} achieve an accuracy of 
83.9\%. Implementing a similar model in a rule-based system like ours would allow 
for some improvements to this result. Their model was trained on a full list of 
Russian words, which is not representative of the words that would be unknown to 
a system like ours. Most of the complicated wordstress patterns are closed 
classes\footnote{The growing number of masculine nouns with shifting stress 
(\emph{d\'{o}ktor$\sim$doktor\'{a}}) are an exception to this generalization.},
so we could exclude closed classes of words from the training data, leaving only
word classes that are likely to be similar to unknown tokens, such as those with 
productive derivational affixes.

Future work/potential applications:
\begin{itemize}
\item As with any lexicon- and rule-based system, those components can be expanded and improved, especially considering the short span over which they were developed.
\item Another relevant issue is whether the ambiguity can be resolved at all. For example, when is stress marked in authentic by-native-for-native texts? A computer should not be expected to predict the stress on such words (although a computer could possibly identify words that should be marked for natives.)
\end{itemize}
%\section*{Acknowledgments}
%
%Do not number the acknowledgment section. Do not include this section
%when submitting your paper for review.
